A Framework for Modelling Thin Objects: \\ from Meshing to Shell Finite Element Method

### 2010-03-09 MICCAI2010/paper.tex
CHG: - changed computation of the error (it's now the actual two-sided Hausdorff distance that is computed) - changed colour gradient (conversion from HSL colours) - simplification of the vertex shader - updates of all screenshots for the paper (with white backgrounds) and better image to illustrate the results on cylinder - added meshes of liverHighRes, liverLowRes300 (coarse mesh) and liverLowRes300(coarse mesh after one iteration) - updates scenes to take the changes into account - loads high res mesh as Vec3d (instead of Rigids), changed made accordingly in ForceField and MechanicalMapping

\begin{figure}
\centering
\includegraphics[height=7cm]{images/cylinderResults}
\caption {(a) Coarse mesh rendered with shells. (b) Gaps between the coarse mesh and the targeted cylinder. (c) New mesh after one iteration of our algorithm. (d) Differences between the two meshes have been subtantially reduced.}
\label{fig-cylinderResults}
\end{figure}

>>>>

\begin{figure}
\centering
\includegraphics[height=4cm]{images/cylinderResults2}
\caption {(Left) Hausdorff distance colour map of the coarse mesh rendered with shells. (Right) Hausdorff distance colour map after one iteration of our algorithm. We can notice that differences with the target mesh have been subtantially reduced.}
\label{fig-cylinderResults}
\end{figure}
